Quantum Oracles - How to Transform Classical Problems into Quantum ones

### 2024-08-05 latex/paper.tex
updated paper

\documentclass{article}
\usepackage{arxiv}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}      
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage{cleveref}       
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
\usepackage{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage{titlesec}
%\usepackage[rightcaption]{sidecap}
\usepackage{wrapfig}
\usepackage{subfig}

@@

\begin{figure}[!ht]
	\centering
	\includegraphics[scale=0.3]{minimal-oracle.png}
	\caption{Boolean Minimal Oracle example}
	\label{fig:minimal-oracle}
\end{figure}

@@

\begin{center}
	\includegraphics[scale=0.3]{QFT_1.png}
	\captionof{figure}{QFT Oracle example}
	\label{fig:QFT}
\end{center}

\begin{center}
	\includegraphics[scale=0.3]{QFT_1_bloch.png}
	\captionof{figure}{Values Mapped onto Fourier basis example (quantum state $\ket{000}$)}
	\label{fig:QFT-bloch}
\end{center}

@@

\begin{center}
	\includegraphics[scale=0.25]{Grover.png}
	\captionof{figure}{Example Grover's algorithm with $3$ Qubits}
	\label{fig:grover-default-circuit}
\end{center}

For building the circuit, is needed a joint of $Oracle + Diffuser$ applied $k$ time, which $k \approx { {\pi \over {4 \sqrt{a\over{2^n}}}} - {1\over2}  }$, being $a$ the number of values marked by the Oracle. Once we want to find just a single file, the use of this relation is not required, being need to apply the algorithm once to find the bit-string.

@@

%FIX THIS IMAGE%
%\begin{SCfigure}[0.45][h]
%	\caption{Comparing the Standard Grover's algorithm with the version modifying the rotation angles $[0, 2\pi]$ for each 4 bits bit-string}
%	\includegraphics[scale=0.45]{improvement-grover-algorithm-4bits-0-to-2pi.png}
%	\label{fig:best-angle-grover}
%\end{SCfigure}

@@

\begin{center}
	\includegraphics[scale=0.4]{new-grover-test-different-bit-strings-with-optimal-angles.png}
	\captionof{figure}{Test Using the best angles of each bit-string in different ones}
	\label{fig:best-angles-diff-bit-strings-grover}
\end{center}

@@

\begin{center}
	\includegraphics[scale=0.5]{classical_grover_for_1_bit_strings_l2_outcomes.png}
	\captionof{figure}{Results for Grover with 2 Qubits (default rotation)}
	\label{fig:l2-grover-classical-outcomes}
\end{center}

@@

\begin{center}
	\includegraphics[scale=0.5]{new_grover_for_1_bit_strings_l2_outcomes.png}
	\captionof{figure}{Results for Grover with 2 Qubits (modified rotation)}
	\label{fig:l2-grover-new-outcomes}
\end{center}

For our purpose in this project, a hybrid algorithm was done. So during the circuit setup, the searched value pass through a Hash-Table will optimal angles. This way, the algorithm can achieve better outcomes at the end of the execution, finding, this way, the file we want.

%FIX: cut the image a little bit on the left sie
%FIND A WAY TO PUT THESE TWO IMAGES ON THE SIDES OF THE PAGE

	\begin{center}
		\centering
		\includegraphics[scale=0.3]{less_than.png}
		\captionof{figure}{Sets Difference Algorithm Example}
		\label{fig:less-than-circuit}
	\end{center}

@@

\begin{center}
	\includegraphics[scale=0.4]{less_than_unitary.png}
	\captionof{figure}{Unitary After applying the Sets Difference algorithm}
	\label{fig:less-than-circuit-unitary}
\end{center}

After Overlapping the phases  \ref{fig:less-than-circuit-unitary}, only the values $\{100, 101\}$ keep the $-1$ value. This way, we can do the set operation just applying some oracles with the values.

\subsubsection{Solução}

>>>>

\documentclass{article}
\usepackage{arxiv}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}    
\usepackage{hyperref}      
\usepackage{url}            
\usepackage{booktabs}       
\usepackage{amsfonts}       
\usepackage{nicefrac}       
\usepackage{microtype}      
\usepackage{cleveref}       
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{doi}
%\usepackage{caption}
\usepackage{braket}
\usepackage{amsmath}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{mathtools}
\usepackage{titlesec}
\usepackage[rightcaption]{sidecap}
\usepackage{wrapfig}
\usepackage{subfig}

@@

\begin{figure}
	\centering
	\includegraphics[scale=0.3]{minimal-oracle.png}
	\caption{Boolean Minimal Oracle example}
	\label{fig:minimal-oracle}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfloat[\centering QFT Oracle example]{\includegraphics[scale=0.3]{QFT_1.png} \label{fig:QFT}}
	\subfloat[\centering Values Mapped onto Fourier basis example (quantum state $\ket{000}$)]{\includegraphics[scale=0.2]{QFT_1_bloch.png} \label{fig:QFT-bloch}}
	\caption{QFT Oracle}
	\label{fig:QFT-oracle}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.25]{Grover.png}
	\caption{Example Grover's algorithm with $3$ Qubits}
	\label{fig:grover-default-circuit}
\end{figure}

For building the circuit, is needed a joint of $Oracle + Diffuser$ applied $k$ time, which $k \approx { {\frac{\pi}{4 \sqrt{\frac{a}{2^n}}}} - {\frac{1}{2}}  }$, being $a$ the number of values marked by the Oracle. Once we want to find just a single file, the use of this relation is not required, being need to apply the algorithm once to find the bit-string.

@@

\begin{SCfigure}[0.6][h]
	\caption{Comparing the Standard Grover's algorithm with the version modifying the rotation angles $[0, 2\pi]$ for each 4 bits bit-string}
	\includegraphics[width=8cm]{improvement-grover-algorithm-4bits-0-to-2pi.png}
	\label{fig:best-angle-grover}
\end{SCfigure}

@@

\begin{figure}[h]
	\centering
	\includegraphics[scale=0.4]{new-grover-test-different-bit-strings-with-optimal-angles.png}
	\caption{Test Using the best angles of each bit-string in different ones}
	\label{fig:best-angles-diff-bit-strings-grover}
\end{figure}

@@

\begin{figure}[h]
	\centering
	\subfloat[\centering Results for Grover with 2 Qubits (default rotation)]{\includegraphics[scale=0.3]{classical_grover_for_1_bit_strings_l2_outcomes.png} \label{fig:l2-grover-classical-outcomes}}
	\subfloat[\centering Results for Grover with 2 Qubits (modified rotation)]{\includegraphics[scale=0.3]{new_grover_for_1_bit_strings_l2_outcomes.png} \label{fig:l2-grover-new-outcomes}}
	\caption{Comparing Grover with 2 qubits using the default and modified rotation}
	\label{fig:comparing-grover-2-qubits}
\end{figure}

For our purpose in this project, the hybrid approach was used. So during the circuit setup, the searched value pass through a Hash-Table will optimal angles. This way, the algorithm can achieve better outcomes at the end of the execution, finding, this way, the file we want.

@@

\begin{figure}[h]
	\centering
	\subfloat[\centering Sets Difference Algorithm Example]{\includegraphics[scale=0.4]{less_than.png} \label{fig:less-than-circuit}}
	\subfloat[\centering Unitary After applying the Sets Difference algorithm]{\includegraphics[scale=0.5]{less_than_unitary.png} \label{fig:less-than-circuit-unitary}}
	\caption{Sets Difference example}
	\label{fig:sets-diff-example}
\end{figure}

@@

After Overlapping the phases  \ref{fig:less-than-circuit-unitary}, only the values $\{100, 101\}$ keep the $-1$ value. This way, we can do the set operation just applying some oracles with the values range we want.

\subsubsection{Final Solution}

As a solution for this problem, a hash function was made, mapping the path of some file $p$ to a specific bit-string $b$ $F: p \to b$
